The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-04-12 paper.tex
Use new working title from AU.
Update acknowledgement and add saxony sigil.

%\pretitle{}
\title{ANNO: The Anthropological Notation Ontology}
\runtitle{Anthropological Notation Ontology}
%\subtitle{}

@@

\begin{ack}
The ANNO project is co-financed with tax funds on the basis of the budget adopted by the Saxon Parliament.
\end{ack}

>>>>

%\pretitle{}
\title{The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes}
\runtitle{Anthropological Notation Ontology}
%\subtitle{}

@@

\begin{ack}
\noindent\begin{minipage}{0.90\textwidth}
The ANNO project is co-financed from tax funds based on the budget passed by the Parliament of the Free State of Saxony.
\end{minipage}%
\hfill%
\begin{minipage}{0.04\textwidth}\raggedleft
\includegraphics[width=\textwidth]{img/saxony.pdf}
\end{minipage}
\end{ack}
